---
title: "Lab-2-RMarkdown-W/-Git"
author: "James B"
date: "08/10/2020"
output: html_document
---

Demonstration of a sine wave in R

# Wave Plot
```{r}

#define x as a vector of numbers between 0 and 20 at 0.01 intervals
x <- seq(0,20,0.01)
# define the values of y as the sin"'"d values in vector x
y <- sin(x)
# create a dataframe out of x and y
sin_df <- data.frame(x, y)
# show the top 10 entries in the data frame
head(sin_df, 10)

```

## Displaying the wave
```{r, echo = FALSE}
#Plot the sin wave but do not display the code doing so
plot(sin_df)
```

# Replicability and Reproducibility
Two important concepts related to the results of scientific studies are replicability and reproducibility. 
Replicability is defined as obtaining consistent results across studies aimed at answering the same scientific question, each of which has obtained its own data, whereas reproducibility means obtaining consistent computational results using the same input data, computational steps, methods, code, and conditions of analysis.

Of these two concepts, reproducibility is the more modest goal, but is surprisingly hard to achieve as data is often not properly formatted or is stored in sub-optimal conditions. Therefore, it is imperative that data scientists and more widely scientists in general adhere to strict guidelines on data formatting and organisation.